Incentives are the biggest barriers to widespread data sharing

### 2021-08-11 new-paper.Rmd
add altered paragraph into metadata section

**Variable names** are short, descriptive names with no spaces or special characters, such as "job_position" or "date". **Variable description** describes the measured variables, e.g., "University Job Position" or "Date Started", and should also define *variable codes* and *missing data*. **Unit text** defines the type of variable recorded (e.g., string, date, numeric, integer), this avoids serious errors of misrepresented data (e.g., a column of a gene sequence being interpreted as a date). A simple metadata file that describes the variable names, variable description, and unit text is a great starting point, and is sometimes known as a codebook.  For more details, see [@Broman2017; @Ellis2017; @Arslan2019]. Metadata can be encoded into more formal plain text formats that follow a set standard, such as EML or SCHEMA-LD. A deep understanding of these formats isn't required to use them, for more details, and guidance on generating them see @Arslan2019.

>>>>

**Variable names** are short, descriptive names with no spaces or special characters, such as "job_position" or "date". **Variable description** describes the measured variables, e.g., "University Job Position" or "Date Started", and should also define *variable codes* and *missing data*. **Unit text** defines the type of variable recorded (e.g., string, date, numeric, integer), this avoids serious errors of misrepresented data (e.g., a column of a gene sequence being interpreted as a date).

A simple metadata file that describes the variable names, variable description, and unit text is a great starting point, and is sometimes known as a codebook. Metadata can be encoded into more formal plain text formats that follow a set standard, such as EML or SCHEMA-LD. A deep understanding of these formats isn't required to use them. For more details, see [@Broman2017; @Ellis2017; @Arslan2019 @Leipzig2021].
